Age-related changes in plant growth and traits

### 2015-09-10 RA_combined_plots.Rmd
various for lab meeting
adding leaf turnover calculations

###Current best plots  
* the plot of investment by leaf area, indicates that allocation to reproduction, leads to less vegetative investment than predicted  
* plotting by age, shows that leaf investment and height growth are curtailed as plants age  
* I think there still needs to be more of a link to connect this decreased "growth" with age directly to reproduction - maybe a "new" version of the plot showing individuals with more reproduction have less growth?
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
pdf("figs2/RA_schedule_plots_2.pdf", height=11.3, width=8)
plot
par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
yvar <- "leaf_area"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

>>>>

###Current best plots  
* the plot of investment by leaf area, indicates that allocation to reproduction, leads to less vegetative investment than predicted  
* plotting by age, shows that leaf investment and height growth are curtailed as plants age  
* I think there still needs to be more of a link to connect this decreased "growth" with age directly to reproduction - maybe a "new" version of the plot showing individuals with more reproduction have less growth?
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
SummaryInd <- SummaryInd[order(factor(SummaryInd$species,levels=c(c("HATE","PELA","BAER","PEPU","LEES","EPMI","COER","PUTU","PHPH","GRBU","GRSP","HEPU","PILI","BOLE")))),]

pdf("figs2/RA_schedule_plots_3.pdf", height=11.3, width=8)
plot
par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
yvar <- "leaf_area"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

### 2015-09-10 tests.Rmd
various for lab meeting
adding leaf turnover calculations

>>>>

```{r}
#pdf("figs2/weight_diameter_segments_2.pdf", height=11.3, width=8)
#plot
par(mfcol=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
data <- subset(HarvestData)
data <- split(data, data$species)

for(spp in names(data)) {
plot(stem_weight~diameter,data[[spp]],log="xy",cex=.7, main=spp,col=col.age(data[[spp]]$age),pch=16,ylab="stem (circle) + leaf (tri)"
)
points(leaf_weight~diameter,data[[spp]],cex=.7,pch=17,col=col.age(data[[spp]]$age))
}
#dev.off()

```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
#pdf("figs2/tradeoff.pdf", height=11.3, width=8)
#plot
par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "growth_stem_diameter"

data <- subset(SummaryInd,RA_leaf_area>0&RA_leaf_area<1.5)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
}

mtext("Stem diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA (leaf area)", 2, outer=TRUE,cex=1.2)  
legend("bottomleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
#dev.off()
```

SummaryInd$leaf_turnover <- SummaryInd$leaf_weight_0/SummaryInd$LL_death
plot(leaf_turnover~age,SummaryInd,log="xy", col=col.spp(species),pch=16)
SummaryInd$leaf_net <- SummaryInd$growth_leaf + SummaryInd$leaf_turnover
plot(leaf_net~age,SummaryInd,log="xy", col=col.spp(species),pch=16)
plot(leaf_turnover~leaf_net,SummaryInd,log="xy", col=col.age(age),pch=16)
abline(0,1)

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfcol=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
yvar <- "leaf_turnover"
xvar <- "leaf_net"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
  abline(0,1)
  abline(log10(.111),1)
  abline(log10(.010101),1)
}
```
